Estimating the Initial Susceptible Fraction in Dengue Dynamics

### 2015-06-15 draft_lm1.tex
sort of solves #30

Dengue is an arthropod-borne febrile disease caused by a flavivirus with four 
serotypes which causes an estimated  $50$ million infections each 
year~\citep{Guzman2010}.
In humans, immunity against  a particular serotype is  considered permanent 
after the exposure and cross immunity to there serotypes is considered short 
lived~\citep{halstead_dengue_2007}.
As a consequence, the proportions of viral serotypes co-circulating at any 
point in time are strongly dependent on previous incidence patterns of the 
disease, which determine the number of individuals susceptible to each serotype 
at any point in time.
% LM: Maybe a citation here?

>>>>

Dengue is an arthropod-borne febrile disease caused by a flavivirus with four 
serotypes which causes an estimated  $50$ million infections each 
year~\citep{Guzman2010}.
In humans, immunity against a particular serotype is considered permanent 
after the exposure and cross immunity to other serotypes is considered short 
lived~\citep{halstead_dengue_2007}.
As a consequence, the proportions of viral serotypes co-circulating at any 
point in time are strongly dependent on previous incidence patterns of the 
disease, which determine the number of individuals susceptible to each serotype 
at any point in time.
% LM: Maybe a citation here?
